Mbh-n paper

### 2015-09-18 papers/ellicular/ellicular.tex
fri

%\title[Intermediate-scale discs]{Early-type galaxies with intermediate-scale discs and their ordinary supermassive black holes}
\title[Ellicular galaxies]{Ellicular galaxies and their (non {\"u}ber-massive) black holes}

@@

\begin{abstract}
The classification early-type galaxy includes both elliptically-shaped and lenticular galaxies, 
with the latter composed of a spheroid, or bulge, of stars encased within a larger, but flatter, stellar disc. 
Theoretically, the spheroid-to-disc flux ratio can assume any positive value. 
However, several studies only consider spheroid/disc decompositions 
in which the disc neatly dominates over the spheroid at large galaxy radii -- creating an inner bulge -- 
and they reject decompositions if the disc remains embedded within the spheroid, labeling them as ``unphysical''. 
Here we show that these rejected models correctly reproduce the photometric and kinematic properties of a class of early-type galaxy 
%with intermediate-scale disc. 
%Intermediate-scale discs have often been confused with large-scale discs, 
%and as a consequence the disc luminosities have been considerably overestimated 
%and their spheroid luminosities underestimated. 
intermediate between that of elliptical and lenticular galaxies, and which we name ellicular galaxies. 
Ellicular galaxies have often been confused with lenticular galaxies, and as a consequence their disc luminosities have been considerably overestimated 
and their spheroid luminosities underestimated. 
This has recently led to some surprising conclusions, 
such as the claim that a number of ellicular galaxies (Mrk 1216, NGC 1277, NGC 1271, and NGC 1332) 
host a central black hole whose mass is abnormally large compared to expectations from the (underestimated) spheroid luminosity. 
When ellicular galaxies are properly modeled, 
they no longer appear as extreme outliers in the (black hole mass)-(spheroid mass) diagram, 
thereby resolving previous anomalies. 
This not only nullifies the need for invoking different evolutionary scenarios for these galaxies 
but it strengthens the significance of the observed (black hole mass)-(spheroid mass) correlation 
and confirms its importance as a fundamental ingredient for theoretical and semi-analytic models 
used to describe the coevolution of spheroids and their central supermassive black holes.

@@

(e.g.~\citealt{khochfarsilk2006,dekel2009nat,ceverino2010,ceverino2012,conselice2012}). 
A thorough review can be found in \citet{combes2014arX,combes2014pro}.

@@

as their nuclear and large-scale homologues and,  
in some cases, they have even been labelled as something ''unphysical''. 

@@

and the impact this has on the important (black hole mass)-to-(spheroid stellar mass) ratio %, $M_{\rm BH}/M_{*,sph}$, 

@@

Identifying the extent of these discs with respect to their spheroid can however be subtle. 

@@

On the one hand, a specific angular momentum profile that is rapidly increasing beyond $1-2$ half-light radii 
is a signature of a large-scale disc. 
On the other hand, a specific angular momentum profile that increases up to $1-2$ half-light radii and declines beyond that point 

@@

(i) a lenticular galaxy, comprised of a large-scale disc and a relatively smaller encased bulge, 

@@

The awareness that many ``elliptical'' galaxies actually contain embedded stellar discs 

@@

more recently, intermediate-scale discs were all but unfamiliar to \cite{kormendybender2012} and \cite{krajnovic2013etal}. 

@@

This unspoken bias has led to the rejection of many spheroid/disc decompositions similar to that illustrated in the middle panel of Figure \ref{fig:model}. 

@@

\section{Intermediate-scale disc galaxies}
\label{sec:gal}
Three examples of ellicular galaxies are Mrk 1216, NGC 1332, and NGC 3115. 
In the following Sections, we present a photometric analysis of these three galaxies, 
and we compare our results with the kinematical analysis (when) available from the literature. 
For the galaxies NGC 1332 and NGC 3115, we used $3.6~\rm \mu m$ images obtained with the InfraRed Array Camera (IRAC) 
onboard the \emph{Spitzer Space Telescope}. 
For the galaxy Mrk 1216, we used an archived Hubble Space Telescope (\emph{HST}) image  
taken with the Wide Field Camera 3 (WFC3) and the near-infrared \emph{F160W} filter ($H$-band). 
Our galaxy decomposition technique is extensively described in Savorgnan \& Graham (\emph{submitted}).
Briefly, the galaxy images were background-subtracted, and masks for contaminating sources were created. 
The one-dimensional Point Spread Function (PSF) was characterized using a Gaussian profile for the \emph{HST} observation 
and a \cite{moffat1969} profile for the \emph{Spitzer} observations.
We performed an isophotal analysis of the galaxies using the IRAF\footnote{IRAF 
is the Image Reduction and Analysis Facility, distributed by the National Optical Astronomy Observatory, 
which is operated by the Association of Universities for Research in Astronomy (AURA) 
under cooperative agreement with the National Science Foundation.} task {\tt ellipse}\footnote{Our analysis 
was performed before {\tt isofit} \citep{ciambur2015} was conceived or available. 
After {\tt isofit} was recently developed and implemented in IRAF, 
we employed it to re-extract the surface brightness profiles of the galaxies NGC 1332 and NGC 3115. 
We then repeated the analysis and checked that this change does not significantly alter our results. 
In fact, although {\tt isofit} provides a more accurate description of the isophotes in presence of an inclined disc, 
the discs of NGC 1332 and NGC 3115 are relatively faint compared to the spheroidal components, 
therefore the differences between the light profile obtained with {\tt ellipse} and that obtained with {\tt isofit} are small. } 
\citep{taskellipse}. 
The galaxy isophotes were modelled with a series of concentric ellipses, 
allowing the ellipticity, the position angle and the amplitude of the fourth harmonic to vary with radius.  
The decomposition of the surface brightness profiles was performed with software written by G. Savorgnan.
We modelled the light profiles with a combination of PSF-convolved analytic functions, 
using one function per galaxy component.

\subsection{NGC 3115}
The presence of a disc in NGC 3115 is obvious due to its edge-on orientation (Figure \ref{fig:n3115}). 
Less obvious is the extent of such disc, if one only relies on a visual inspection of the galaxy image. 
The ellipticity profile is consistent with the presence of an intermediate-scale disc. 
Moreover, the kinematics of NGC 3115 \citep{arnold2011n3115} also disprove the presence of a large scale disc, 
because the galaxy is rapidly rotating only within two galaxy half-light radii ($\sim 2 \times 50~\rm arcsec$), 
whereas the rotation significantly drops at larger radii.  
The unsharp mask of NGC 3115 (Figure \ref{fig:n3115}) betrays the presence of a fain edge-on nuclear ring, 
which can also be spotted as a small peak in the ellipticity profile 
(at semimajor-axis lenght $R_{\rm maj} \sim 15~\rm arcsec$).
The spheroidal component of NGC 3115 is well described with a \cite{sersic1963} profile.
The highly inclined intermediate-scale disc is better fit with a $n<1$ S\'ersic profile 
(the S\'ersic index $n$ regulates the curvature of the S\'ersic profile) 
rather than with an exponential function, 
as explained by \cite{pastrav2013a}. 
The nuclear ring is modelled with a Gaussian function.

@@

Recently, a handful of ellicular galaxies have been claimed to host \emph{{\"u}ber-massive} black holes, 

>>>>

%\title[Intermediate-scale discs]{Early-type galaxies with intermediate-scale discs and their ordinary supermassive black holes}
\title[Ellicular galaxies]{Ellicular galaxies and their (non over-massive) black holes}

@@

\begin{abstract}
The classification ``early-type'' galaxy includes both elliptically- and lenticular-shaped galaxies, 
with the latter composed of a spheroidal stellar system encased within a larger, but flatter, stellar disc. 
Theoretically, the spheroid-to-disc flux ratio can assume any positive value,  
but in practice studies often consider only spheroid/disc decompositions 
in which the disc neatly dominates over the spheroid at large galaxy radii, 
creating an inner ``bulge'' as observed in most spiral galaxies. 
Here we reveal that decompositions in which the disc remains embedded within the spheroid, labelled by some as ``unphysical'',  
correctly reproduce both the photometric and kinematic properties of a class of early-type galaxy 
intermediate between that of elliptical and lenticular galaxies, which we refer to as \emph{ellicular} galaxies for ease of reference. 
Ellicular galaxies have often been confused with lenticular galaxies, 
such that %their disc luminosities have been considerably overestimated 
their spheroid luminosities have been considerably underestimated. 
This has recently led to some surprising conclusions, 
such as the claim that a number of ellicular galaxies (e.g.~Mrk 1216, NGC 1277, NGC 1271, and NGC 1332) 
host a central black hole whose mass is abnormally large compared to expectations from the (underestimated) spheroid luminosity. 
We show that when ellicular galaxies are correctly modeled, 
they no longer appear as extreme outliers in the (black hole mass)-(spheroid mass) diagram. 
This not only nullifies the need for invoking different evolutionary scenarios for these galaxies 
but it strengthens the significance of the observed (black hole mass)-(spheroid mass) correlation 
and confirms its importance as a fundamental ingredient for theoretical and semi-analytic models 
used to describe the coevolution of spheroids and their central supermassive black holes.

@@

(e.g.~\citealt{whiterees1978,khochfarsilk2006,dekel2009nat,ceverino2010,ceverino2012,conselice2012}), 
and a thorough review can be found in \citet{combes2014arX,combes2014pro}.

@@

as their nuclear and large-scale homologues and 
they have at times been labelled and rejected as ''unphysical'' when detected. 

@@

and the impact this has on the (black hole mass)-to-(spheroid stellar mass) ratio %, $M_{\rm BH}/M_{*,sph}$, 

@@

Identifying the radial extent of these discs with respect to the spheroid can however be subtle. 

@@

A specific angular momentum profile that is rapidly increasing beyond $1-2$ half-light radii 
is a signature of a large-scale disc, 
while a specific angular momentum profile that increases up to $1-2$ half-light radii and then declines beyond that point 

@@

(i) a lenticular galaxy comprised of a large-scale disc and a relatively smaller encased bulge, 

@@

The awareness that many so-called ``elliptical'' galaxies actually contain stellar discs 

@@

more recently, intermediate-scale discs were anything but unfamiliar to \cite{kormendybender2012} and \cite{krajnovic2013etal}. 

@@

This bias has led to the rejection of many spheroid/disc decompositions similar to that illustrated in the middle panel of Figure \ref{fig:model}. 

@@

\section{Intermediate-scale disc galaxies}
\label{sec:gal}
Three examples of ellicular galaxies are Mrk 1216, NGC 1332, and NGC 3115. 
In the following Sections, we present a photometric analysis of these three galaxies, 
and we compare our results with the kinematical analysis available from the literature for Mrk 1216 and NGC 3115. 
For the galaxies NGC 1332 and NGC 3115, we used $3.6~\rm \mu m$ images obtained with the InfraRed Array Camera (IRAC) 
onboard the \emph{Spitzer Space Telescope}. 
For the galaxy Mrk 1216, we used an archived Hubble Space Telescope (\emph{HST}) image  
taken with the Wide Field Camera 3 (WFC3) and the near-infrared \emph{F160W} filter ($H$-band). 
Our galaxy decomposition technique is extensively described in Savorgnan \& Graham (2015).
Briefly, the galaxy images were background-subtracted, and masks for contaminating sources were created. 
The one-dimensional Point Spread Function (PSF) was characterized using a Gaussian profile for the \emph{HST} observation 
and a \cite{moffat1969} profile for the \emph{Spitzer} observations.
We performed an isophotal analysis of the galaxies using the IRAF\footnote{IRAF 
is the Image Reduction and Analysis Facility, distributed by the National Optical Astronomy Observatory, 
which is operated by the Association of Universities for Research in Astronomy (AURA) 
under cooperative agreement with the National Science Foundation.} task {\tt ellipse}\footnote{Our analysis 
was performed before {\tt isofit} \citep{ciambur2015} was conceived or available. 
After {\tt isofit} was recently developed and implemented in IRAF, 
we employed it to re-extract the surface brightness profiles of the galaxies NGC 1332 and NGC 3115. 
We then repeated the analysis and checked that this change does not significantly alter our results. 
In fact, although {\tt isofit} provides a more accurate description of the isophotes in presence of an inclined disc, 
the discs of NGC 1332 and NGC 3115 are relatively faint compared to the spheroidal components, 
therefore the differences between the light profile obtained with {\tt ellipse} and that obtained with {\tt isofit} are small. } 
\citep{taskellipse}. 
The galaxy isophotes were modelled with a series of concentric ellipses, 
allowing the ellipticity, the position angle and the amplitude of the fourth harmonic to vary with radius.  
The decomposition of the surface brightness profiles was performed with software written by G. Savorgnan 
and described in Savorgnan \& Graham (2015).
We modelled the light profiles with a combination of PSF-convolved analytic functions, 
using one function per galaxy component.

\subsection{NGC 3115}
The presence of a disc in NGC 3115 is obvious due to its edge-on orientation (Figure \ref{fig:n3115}). 
Less obvious is the radial extent of this disc, if one only relies on a visual inspection of the galaxy image. 
The ellipticity profile (Figure \ref{fig:n3115}) is consistent with the presence of an intermediate-scale disc. 
Moreover, the kinematics of NGC 3115 \citep{arnold2011n3115} also disprove the presence of a large-scale disc, 
because the galaxy is rapidly rotating only within two galaxy half-light radii ($\sim 2 \times 50~\rm arcsec$), 
and the rotation significantly drops at larger radii.  
The unsharp mask of NGC 3115 (Figure \ref{fig:n3115}) betrays the presence of a faint edge-on nuclear ring, 
which can also be spotted as a small peak in the ellipticity profile 
(at semimajor-axis length $R_{\rm maj} \sim 15~\rm arcsec$).
The spheroidal component of NGC 3115 is well described with a \cite{sersic1963} profile.
The highly inclined intermediate-scale disc is better fit with an $n<1$ S\'ersic profile 
(the S\'ersic index $n$ regulates the curvature of the S\'ersic profile) 
rather than with an exponential function, 
as explained by \cite{pastrav2013a}. 
The nuclear ring is modelled with a Gaussian function. 
In comparison,

@@

Recently, a handful of ellicular galaxies have been claimed to host \emph{over-massive} black holes, 

### 2015-09-18 papers/mbhn/mbhn.tex
fri

\section{Introduction}

>>>>

\section{Introduction}
The empirical \cite{sersic1963,1968} model has been demonstrated to provide adequate description 
of the light distribution of the stellar spheroidal component of galaxies, 
yet its physical intepretation has remained unknown for decades.

origin of L-n \\
M-L + L-n ... M-n \\
M-C and M-n \\
s+11 v+12 b+12 \\
my paper \\
paper I and II \\
